### 2021-10-05 paper.Rmd
some work on paper

    Anticlustering refers to a collection of methods that partition data sets into disjunct groups with two primary goals: (a) high between-group similarity and (b) high within-group heterogeneity. Some anticlustering objectives simultaneously pursue both goals while other methods focus on a particular aspect. The present paper introduces a novel bicriterion objective aiming at optimizing between-group similarity. *K-plus anticlustering* is an extension of k-means anticlustering, which minimizes the difference between mean values of numeric attributes across clusters. The k-plus objective extends k-means by including a term that aims to optimize similarity with regard to the variance of data across groups, which is ignored by k-means. Surprisingly, it is shown that the combined objective (i.e., the bicriterion) can be reduced to an augmentation of the input data, leaving the original k-means criterion unchanged. Tests on simulated and real data show that k-plus anticlustering usually achieves high similarity both with regard to mean attribute values as well as the variance, with no noticable sacrifice to either criterion. The k-plus extension is therefore preferred over classical k-means anticlustering for optimizing between-group similarity.

@@

Anticlustering objectives differ in the assumed input data and their mathematical definition of cluster similarity. Some anticlustering objectives employ pairwise dissimilarity ratings to compute a total measure of cluster (dis)similarity. The most prominent criterion of this kind is the *diversity*, which is the total sum of dissimilarities between any elements within the same group. Maximizing the diversity simultaneously optimizes within-group heterogeneity as well as between-group similarity.  Because the diversity is the reversal of the clustering editing objective [@zahn1964; @shamir2004vf], @papenberg2020 used the term *anticluster editing* to refer to anticlustering approaches that optimize the diversity. Another important criterion based on pairwise dissimilarities is the *dispersion*, i.e., the minimum dissimilarity between any two elements within the same group [@fernandez2013; @brusco2019]. Maximizing the dispersion increases the within-group heterogeneity by ensuring that any two elements as dissimilar from each other as possible.

Oftentimes, the data available to researchers does not represent pairwise similarity, but numeric, categorical or binary attributes [@dry2009]. That is, the data is a two-way two-mode [@arabie1992] table where rows represent the entities of study, and columns represent variables describing the elements. For example, numeric ratings may describe the attributes of word stimuli for psycholinguistic experiments. Such data may include norms for imagery, concreteness and orthographic variables [@friendly1982]. In other cases, attributes are binary and may represent the presence or absence of a feature [@tversky1977]. In the context of anticlustering, One possible approach for handling two-way two-mode data is to compute an appropriate dissimilarity measure such as the pairwise Euclidean or squared Euclidean distance across a set of numeric attributes [@brusco2019]. Then, anticlustering criteria based on pairwise dissimilarities such as the dispersion or diversity can be optimized to partition the elements into groups.

A different approach to anticlustering directly works with the two-way two-mode feature data using the k-means criterion. K-means is probably the best-known clustering method and its reversal has been recognized as a useful anticlustering tool by Späth [-@spath1986] and Valev [-@valev1998; -@valev1983]. In k-means clustering, the sum of the squared Euclidean distances between elements and the center of the cluster they are assigned to is minimized [@brusco2006branch], usually using the k-means heuristic [@jain2010; @steinley2006]. Minimizing the k-means criterion simultaneously maximizes between-cluster separation and within-cluster homogeneity [@aloise2009np]. For the anticlustering application, the k-means criterion is maximized instead, thereby achieving similarity between groups. Specifically, as @spath1986 noted, k-means anticlustering minimizes differences with regard to the means of the numeric attributes across clusters. Hence, groups are similar with regard to the mean of the distribution of the numeric attributes wheras other parameters---such as the variance---are ignored. When requiring that groups are overall similar to each other, this focus may be misguided as similar means can be obtained even when the underlying distributions are different [@anscombe1973]. @papenberg2020, showed that maximizing the diversity (based on the pairwise Euclidean distances) is better suited to minimize difference with regard to both the mean and the variance of the data; it was shown that even an entirely random split usually resulted in more similar variances because k-means solely focuses on the mean similarity.

To optimize overall group similarity---and hence to overcome the limitations of k-means anticlustering---I present k-plus anticlustering in this paper. The k-plus criterion is an extension of the k-means objective that includes a term aiming at optimizing similarity with regard to the variance of data across groups. Interestingly, this bicriterion reformulation can be understood as an augmentation of the original data matrix, leaving the original k-means objective unchanged. I show that the k-plus criterion outperforms other anticlustering criteria when the goal is the minimize difference with regard to the mean and variance of the different groups. In most cases, both objectives can be optimized satisfactorily at the same time without any loss on either. In several examples I illustrate how readers can use k-plus anticlustering easily using the free and open source software anticlust, which is an extension to the statistical programming language R [@papenberg2020].

@@

For the purpose of problem formalization, I adopt the notation @steinley2006 provided in his comprehensive synthesis of half a century of research on k-means. K-means clustering (and anticlustering) is used to partition two-way, two-mode data into groups. That is, $N$ elements each having $P$ attributes are assigned to $K$ groups $(C_1., \ldots, C_K)$, $C_k$ being the set of $n_k$ objects in group $k$. The partitioning is subject to the requirement that each element is assigned to exactly one group, formalized by the following two constraints:

@@

For a data matrix $\mathbf{X}_{N \times P} = \{x_{ij}\}_{N \times P}$, k-means anticlustering aims to maximize the error sum of squares (SSE), which is the sum of the squared Euclidean distances between each data point and its cluster centroid:

@@

Note there is a direct connection between the $SSE$ and the location of the cluster centroids [@spath1986]. If the $SSE$ is minimal---which is the goal of k-means *clustering*---, the centroid values $\overline{\mathbf{x}}^{(k)} (k = 1, \ldots, K)$ are as far away as possible from the overall data centroid $\overline{\mathbf{x}} = (\overline{\mathbf{x}}_1, \overline{\mathbf{x}}_2, \ldots, \overline{\mathbf{x}}_P$), where $\overline{\mathbf{x}}_p$ is the overall mean value on the $p$th attribute:

@@

If the $SSE$ is maximal---which is the goal of k-means *anticlustering*---, the cluster centroids are as close as possible to the overall centroid $\overline{\mathbf{x}}$ and therefore to each other [@spath1986]. Thus, k-means anticlustering directly optimizes the similarity of the mean attribute values across clusters.

@@

In the following, I present a rather straight-forward adaption of the $SSE$ to quantify how the variance of numeric data differs between groups. To motivate the new criterion, we first consider a set of one-dimensional observations $(x_1, \ldots, x_N)$. The extension to the general case of $P$ attributes will be straight-forward.

@@

Because the sample variance is basically defined as an average, k-means anticlustering can be employed to equalize the variance across groups. That is, we can formulate an adaption of the $SSE$ to quantify the degree to which the variance differs between groups. First, however, we generalize the idea to the case of $P$ attributes. For each attribute, we have to compute the squared deviation between all values and the mean of the attribute. We obtain a new data matrix $\mathbf{Y}_{N \times P} = \{y_{ij}\}_{N \times P}$, where

@@

Analogously to the standard $SSE$, the centroid values $\overline{y}_j ^{(k)}$ are given as:

@@

It is unlikely that an exclusive optimization of $SSE_{Var}$ (i.e., equalizing variances) is of interest without also considering the $SSE$ (i.e., equalizing means). A combination of $SSE_{Var}$ and $SSE$, however, can be employed to simultaneously optimize both objectives, which is a reasonable idea when striving for overall cluster similarity. The most simple approach for such a bicriterion optimization is the weighted sum approach [@naidu2014; @marler2010]. That is, both criteria are computed independently from each other and then combined into a single criterion through a weighted sum:

@@

This formula again has the same form as $SSE$ (and $SSE_{Var}$), but is computed on different data. In this case, both the original data $x_{ij}$ as well as the squared distances $y_{ij}$ are used as attributes that enter the objective function. That is, computing the k-plus criterion can be done by first computing the values $y_{ij}$, appending these to the original data matrix, and then computing the $SSE$ on the augmented data matrix. Hence, k-plus anticlustering reduces to an augmentation of the data matrix, leaving the original k-means criterion unchanged.

Note that a problem may arise if the weights $w_1$ and $w_2$ are ignored when optimizing the k-plus objective. Since the computation of the data matrix $\mathbf{Y}_{N \times P}$ involves squaring, the squared distances $y_{ij}$ have much larger values, on average, than the raw values $x_{ij}$ (also see Figure 1). Therefore, the $SSE_{Var}$ criterion naturally receives greater weight when computing $\mathit{SSE_{kplus}}$ than the standard $SSE$ criterion. This imbalance is most likely unwarranted because optimizing similarity with regard to variances is not more important than optimizing similarity with regard to means. A solution is to standardize all values $x_{ij}$ and $y_{ij}$ to the same scale before computing $SSE_{kplus}$, e.g. via $z$-standardization.

@@

When optimizing a bicriterion objective such as $SSE_{kplus}$, the ideal outcome would be to find a partition where both the means and the variances are very similar between groups, i.e., a which partition where both the standard $SSE$ and $SSE_{Var}$ are close to the global optimum value. Generally, research on multi-objective optimization has shown that cases are rare where a single solution satisfies all criteria to an optimal degree [@ferligoj1992direct]. Usually, a tradeoff is necessary. For anticlustering, a motivating example illustrates that aiming to simultaneously optimize similarity of means and variances is not only desirable, but may actually be feasible.

@@

For this motivating example, I created 14 data points following a univariate normal distribution ($M = 15$, $SD = 3$) and then generated all `r n_partitions(14, 2)` possible ways to partition the 14 data points into $K = 2$ equal-sized groups. Figure 1 shows the scatterplot of the criteria $SSE$ and $SSE_{Var}$ across partitions. Note that for both criteria, a larger value is better, i.e., indicates higher similarity with regard to means and variances, respectively. Therefore, to obtain overall between-group similarity, a partition should be chosen that is depicted in the upper right corner of the scatterplot. However, optimal k-means anticlustering would create two groups that are not particularly similar with regard to their variance. The partition that is represented by the squared symbol has the overall best highest $SSE$, but is outperformed by many other partitions with regard to $SSE_{Var}$. Similarly, the partition that maximizes $SSE_{Var}$ (the triangular symbol in Figure 1) is not well-suited to optimize SSE at the same time. The diamond symbol represents the partition that maximizes (the unweighted) $SSE_{kplus}$, i.e., the sum of $SSE$ and $SSE_{Var}$. This partition is located in the right upper corner and yields `r df$kmeans[which.max(df$kplus)] / max(df$kmeans) * 100`% of the global maximum $SSE$, and `r df$kvar[which.max(df$kplus)] / max(df$kvar) * 100`% of the global maximum value of $SSE_{Var}$.

@@

To systematically evaluate the new k-plus criterion, I compared three anticlustering approaches in a simulation study: (a) k-means anticlustering, optimizing the $SSE$; (b) k-plus anticlustering, optimizing the $SSE_{kplus}$; (c) anticluster editing, optimizing the diversity criterion. All methods employed an a priori standardization of the data sets. In the case of k-plus anticlustering, this means that the augmented input data (i.e., the original data and the squared distance data) were subjected to a standardization, which is recommended.

@@

Two primary performance criteria were assessed. First, for k-plus anticlustering, I checked how well the identified solution approximated the ordinary k-means criterion. Specifically, I computed the $SSE$ for the solution that was returned by k-means anticlustering---that directly optimizes $SSE$---and for the solution that was returned by k-plus anticlustering that only indirectly optimizes $SSE$ through $SSE_{kplus}$. If optimizing $SSE_{kplus}$ simultaneously optimizes the standard $SSE$ to a satisfactory degree, we may conclude that simultaneously striving for similar means and variances is feasible by optimizing the k-plus criterion.

@@

Table 1 shows the results of the anticlustering application by listing the descriptive statistics (means and standard deviations) for each of the 9 groups and for each of the 3 features. Additionaly, Table 1 shows the descriptive statistics for an application of k-means anticlustering and anticluster editing (which maximizes the diversity criterion). It is shown that---up to two decimals---k-plus anticlustering perfectly matched all groups with regard to the features' means and standard deviations. K-means anticlustering also perfectly matched the mean values, but showed decreased performance with regard to similarity in standard deviations. Anticluster editing was also well-suited to match both means and standard deviations, but was slightly outperformed by k-plus. The latter result is not surprising because---unlike k-plus anticlustering---anticluster editing does not directly maximize similarity with regard to the means and standard deviations.

>>>>

    Anticlustering refers to a collection of methods that partition data sets into disjunct while addressing two objectives: (a) high between-group similarity and (b) high within-group heterogeneity. For some anticlustering formulations, these two objectives coincide: high between-group similarity is achieved when within-group heterogeneity is maximized. Other anticlustering methods focus on one of the two aspects. The present paper focuces on maximizing between-group similarity by introducing a novel bicriterion objective. *K-plus anticlustering* is an extension of k-means anticlustering, which minimizes the difference between the mean of numeric attributes across clusters. The k-plus objective extends k-means by adding a term that aims to optimize similarity with regard to the variance of the attributes data across clusters. It is shown that the combined bicriterion objective can be reduced to an augmentation of the input data, leaving the original k-means criterion unchanged. A computer simulation and practical examples on real data show that k-plus anticlustering usually achieves high similarity both with regard to mean attribute values as well as the variance, with no noticable sacrifice to either criterion. The k-plus extension is therefore preferred over classical k-means anticlustering for optimizing between-group similarity. K-plus anticlustering is easily accessible to researchers and practitioners: the method has been implemented as part of the open source R package `anticlust`, which is freely available via CRAN (https://cran.r-project.org/package=anticlust) and Github (https://github.com/m-Py/anticlust).

@@

Anticlustering methods can be distinguished by the input data (pairwise dissimilarity vs. attributes values) and the objective function that is used to optimize group between-group similarity or within-group heterogeneity. The most prominent criterion on the basis of pairwise dissimilarity ratings is the *diversity*, i.e., the total sum of dissimilarities between any elements within the same group. Maximizing the diversity simultaneously optimizes within-group heterogeneity and between-group similarity. Because the diversity is the reversal of the clustering editing objective [@zahn1964; @shamir2004vf], @papenberg2020 used the term *anticluster editing* to refer to anticlustering approaches that optimize the diversity. Another important criterion based on pairwise dissimilarities is the *dispersion*, i.e., the minimum dissimilarity between any two elements within the same group [@fernandez2013; @brusco2019]. Maximizing the dispersion increases the within-group heterogeneity by ensuring that any two elements as dissimilar from each other as possible.

Oftentimes, the data available to researchers does not represent pairwise similarity, but numeric, categorical or binary attribute values (or *features*; @dry2009). That is, the data is a two-way two-mode [@arabie1992] table where rows represent the entities of study, and columns represent variables describing the elements. For example, numeric ratings may describe the attributes of word stimuli for psycholinguistic experiments. Such data may include norms for imagery, concreteness and orthographic variables [@friendly1982]. In other cases, attributes are binary and may represent the presence or absence of a facial feature [@tversky1977]. In the context of anticlustering, one possible approach for handling two-way two-mode data is to compute an appropriate dissimilarity measure such as the pairwise Euclidean or squared Euclidean distance across a set of numeric attributes [@brusco2019]. Subsequently, an anticlustering criterion such as the diversity can be optimized to partition the elements into similar groups.

A different approach to anticlustering directly works with the two-way two-mode feature data by maximizing the k-means criterion. K-means is probably the best-known clustering method. Reversing the k-means objective function---using maximization instead of minimization---has been recognized as a useful anticlustering tool by Späth [-@spath1986] and Valev [-@valev1998; -@valev1983]. In k-means clustering, the sum of the squared Euclidean distances between elements and the center of the cluster they are assigned to is minimized [@brusco2006branch], usually using the k-means heuristic [@jain2010; @steinley2006]. Minimizing the k-means criterion simultaneously maximizes between-cluster separation and within-cluster homogeneity [@aloise2009np]. For the anticlustering application, the k-means criterion is maximized instead, thereby achieving similarity between groups. Specifically, as @spath1986 noted, k-means anticlustering minimizes differences with regard to the means of the numeric attributes across clusters. Hence, groups are similar with regard to the mean of the distribution of the numeric attributes wheras other parameters---such as the variance---are ignored. When requiring that groups are overall similar to each other, this focus may be misguided as similar means can be obtained even when the underlying distributions are different [e.g., @anscombe1973]. @papenberg2020, showed that maximizing the diversity (based on the Euclidean distance) is better suited to minimize difference with regard to both the mean and the variance of the data; it was shown that even an entirely random split usually resulted in more similar variances because k-means solely focuses on the mean similarity.

To optimize overall group similarity---and hence to overcome the limitations of k-means anticlustering---I present k-plus anticlustering in this paper. The k-plus criterion is an extension of the k-means objective that includes a term aiming at optimizing similarity with regard to the variance of data across groups. Interestingly, this bicriterion reformulation can be understood as an augmentation of the original data matrix, leaving the original k-means objective unchanged. I show that the k-plus criterion outperforms other anticlustering criteria when aiming at minimizing differences with regard to the mean and the variance of the different groups. In most cases, both objectives can be optimized satisfactorily at the same time without any loss on either. Moreover, in two pratical examples I illustrate how readers can easily apply k-plus anticlustering using the free and open source software `anticlust`, which is an extension to the popular statistical programming language R [@papenberg2020; @R-base; @R-anticlust].

@@

For the purpose of problem formalization, I adopt the notation @steinley2006 provided in his comprehensive synthesis of half a century of research on k-means. K-means clustering (and anticlustering) is used to partition two-way, two-mode data into groups. That is, $N$ elements each having $P$ attributes are assigned to $K$ groups $(C_1., \ldots, C_K)$, $C_k$ being the set of $n_k$ objects in group $k$. The partitioning is subject to the requirement that each element is assigned to exactly one group, formalized by the following two constraints [@papenberg2020]:

@@

For a data matrix $\mathbf{X}_{N \times P} = \{x_{ij}\}_{N \times P}$, k-means anticlustering aims to maximize the error sum of squares ($\mathit{SSE}$), which is the sum of the squared Euclidean distances between each data point and its cluster centroid:

@@

Note there is a direct connection between the $\mathit{SSE}$ and the location of the cluster centroids [@spath1986]. If the $\mathit{SSE}$ is minimal---which is the goal of k-means *clustering*---, the centroid values $\overline{\mathbf{x}}^{(k)} (k = 1, \ldots, K)$ are as far away as possible from the overall data centroid $\overline{\mathbf{x}} = (\overline{\mathbf{x}}_1, \overline{\mathbf{x}}_2, \ldots, \overline{\mathbf{x}}_P$), where $\overline{\mathbf{x}}_p$ is the overall mean value on the $p$th attribute:

@@

If the $\mathit{SSE}$ is maximal---which is the goal of k-means *anticlustering*---, the cluster centroids are as close as possible to the overall centroid $\overline{\mathbf{x}}$ and therefore to each other [@spath1986]. Thus, k-means anticlustering directly optimizes the similarity of the mean attribute values across clusters.

@@

In the following, I present a variation of the $\mathit{SSE}$ that quantifies how the variance of numeric data differs between groups. To motivate the new criterion, we first consider a set of one-dimensional observations $(x_1, \ldots, x_N)$. The extension to the general case of $P$ attributes will be straight-forward.

@@

Because the sample variance is basically defined as an average, k-means anticlustering can be employed to equalize the variance across groups. That is, we can formulate an adaption of the $\mathit{SSE}$ to quantify the degree to which the variance differs between groups. First, however, we generalize the idea to the case of $P$ attributes. For each attribute, we have to compute the squared deviation between all values and the mean of the attribute. We obtain a new data matrix $\mathbf{Y}_{N \times P} = \{y_{ij}\}_{N \times P}$, where

@@

Analogously to the standard $\mathit{SSE}$, the centroid values $\overline{y}_j ^{(k)}$ are given as:

@@

It is unlikely that an exclusive optimization of $SSE_{Var}$ (i.e., equalizing variances) is of interest without also considering the $\mathit{SSE}$ (i.e., equalizing means). A combination of $SSE_{Var}$ and $\mathit{SSE}$, however, can be employed to simultaneously optimize both objectives, which is a reasonable idea when striving for overall cluster similarity. The most simple approach for such a bicriterion optimization is the weighted sum approach [@naidu2014; @marler2010]. That is, both criteria are computed independently from each other and then combined into a single criterion through a weighted sum:

@@

This formula again has the same form as $\mathit{SSE}$ (and $SSE_{Var}$), but is computed on different data. In this case, both the original data $x_{ij}$ as well as the squared distances $y_{ij}$ are used as attributes that enter the objective function. That is, computing the k-plus criterion can be done by first computing the values $y_{ij}$, appending these to the original data matrix, and then computing the $\mathit{SSE}$ on the augmented data matrix. Hence, k-plus anticlustering reduces to an augmentation of the data matrix, leaving the original k-means criterion unchanged.

Note that a problem may arise if the weights $w_1$ and $w_2$ are ignored when optimizing the k-plus objective. Since the computation of the data matrix $\mathbf{Y}_{N \times P}$ involves squaring, the squared distances $y_{ij}$ have much larger values, on average, than the raw values $x_{ij}$ (also see Figure 1). Therefore, the $SSE_{Var}$ criterion naturally receives greater weight when computing $\mathit{SSE_{kplus}}$ than the standard $\mathit{SSE}$ criterion. This imbalance is most likely unwarranted because optimizing similarity with regard to variances is not more important than optimizing similarity with regard to means. A solution is to standardize all values $x_{ij}$ and $y_{ij}$ to the same scale before computing $SSE_{kplus}$, e.g. via $z$-standardization.

@@

When optimizing a bicriterion objective such as $SSE_{kplus}$, the ideal outcome would be to find a partition where both the means and the variances are very similar between groups, i.e., a which partition where both the standard $\mathit{SSE}$ and $SSE_{Var}$ are close to the global optimum value. Generally, research on multi-objective optimization has shown that cases are rare where a single solution satisfies all criteria to an optimal degree [@ferligoj1992direct]. Usually, a tradeoff is necessary. For anticlustering, a motivating example illustrates that aiming to simultaneously optimize similarity of means and variances is not only desirable, but may actually be feasible.

@@

For this motivating example, I created 14 data points following a univariate normal distribution ($M = 15$, $SD = 3$) and then generated all `r n_partitions(14, 2)` possible ways to partition the 14 data points into $K = 2$ equal-sized groups. Figure 1 shows the scatterplot of the criteria $\mathit{SSE}$ and $SSE_{Var}$ across partitions. Note that for both criteria, a larger value is better, i.e., indicates higher similarity with regard to means and variances, respectively. Therefore, to obtain overall between-group similarity, a partition should be chosen that is depicted in the upper right corner of the scatterplot. However, optimal k-means anticlustering would create two groups that are not particularly similar with regard to their variance. The partition that is represented by the squared symbol has the overall best highest $\mathit{SSE}$, but is outperformed by many other partitions with regard to $SSE_{Var}$. Similarly, the partition that maximizes $SSE_{Var}$ (the triangular symbol in Figure 1) is not well-suited to optimize SSE at the same time. The diamond symbol represents the partition that maximizes (the unweighted) $SSE_{kplus}$, i.e., the sum of $\mathit{SSE}$ and $SSE_{Var}$. This partition is located in the right upper corner and yields `r df$kmeans[which.max(df$kplus)] / max(df$kmeans) * 100`% of the global maximum $\mathit{SSE}$, and `r df$kvar[which.max(df$kplus)] / max(df$kvar) * 100`% of the global maximum value of $SSE_{Var}$.

@@

To systematically evaluate the new k-plus criterion, I compared three anticlustering approaches in a simulation study: (a) k-means anticlustering, optimizing the $\mathit{SSE}$; (b) k-plus anticlustering, optimizing the $SSE_{kplus}$; (c) anticluster editing, optimizing the diversity criterion. All methods employed an a priori standardization of the data sets. In the case of k-plus anticlustering, this means that the augmented input data (i.e., the original data and the squared distance data) were subjected to a standardization, which is recommended.

@@

Two primary performance criteria were assessed. First, for k-plus anticlustering, I checked how well the identified solution approximated the ordinary k-means criterion. Specifically, I computed the $\mathit{SSE}$ for the solution that was returned by k-means anticlustering---that directly optimizes $\mathit{SSE}$---and for the solution that was returned by k-plus anticlustering that only indirectly optimizes $\mathit{SSE}$ through $SSE_{kplus}$. If optimizing $SSE_{kplus}$ simultaneously optimizes the standard $\mathit{SSE}$ to a satisfactory degree, we may conclude that simultaneously striving for similar means and variances is feasible by optimizing the k-plus criterion.

@@

Table 1 shows the results of the anticlustering application by listing the descriptive statistics (means and standard deviations) for each of the 9 groups and for each of the 3 features. Additionaly, Table 1 shows the descriptive statistics for an application of k-means anticlustering and anticluster editing (which maximizes the diversity criterion). It is shown that---up to two decimals---k-plus anticlustering perfectly matched all groups with regard to the features' means and standard deviations. K-means anticlustering also perfectly matched the mean values, but showed decreased performance with regard to similarity in standard deviations. Anticluster editing was also well-suited to match both means and standard deviations, but was slightly outperformed by k-plus. The latter result is not surprising because---unlike k-plus anticlustering---anticluster editing does not directly maximize similarity with regard to the means and standard deviations, but instead optimizes the within-group heterogeneity.
